### 2019-04-16 Rapport/TG_ITA/Bibliographic_analysis/Coursera.tex
Coursera Ex 6

	Missclassification error: 
\begin{equation}
	err(h_\theta(x),y) = 
	\begin{cases}
      1 & $ if $ h_\theta(x) \geq 0.5$ and $y=0$ or $h_\theta(x) < 0.5$ and $y = 1 \\
      0 & $otherwise$ 
   \end{cases}

\end{equation}

@@

	Overfittin the data  = low $\lambda$
	\begin{enumerate}
	\item Create a list of lambdas (i.e. λ∈{0,0.01,0.02,0.04,0.08,0.16,0.32,0.64,1.28,2.56,5.12,10.24});
\item Create a set of models with different degrees or any other variants.
\item Iterate through the $\lambda$ and for each $\lambda$ go through all the models to learn some $\Theta$.
\item Compute the cross validation error using the learned $\Theta$ (computed with $\lambda$) on the $J_{cv}(\Theta)$ without regularization or $\lambda = 0$.
\item Select the best combo that produces the lowest error on the cross validation set.
\item Using the best combo $\Theta$ and $\lambda$, apply it on $J_{test}(\Theta)$ to see if it has a good generalization of the problem.
	\end{enumerate}

@@

	\begin{enumerate}
	\item Getting more training examples: Fixes high variance
\item Trying smaller sets of features: Fixes high variance
\item Adding features: Fixes high bias
\item Adding polynomial features: Fixes high bias
\item Decreasing λ: Fixes high bias
\item Increasing λ: Fixes high variance.
	\end{enumerate}

@@

A large neural network with more parameters is prone to overfitting. It is also computationally expensive. In this case you can use regularization (increase λ) to address the overfitting.

@@

>>>>

	Missclassification error: 
%\begin{equation}
%	err(h_\theta(x),y) = 
%	\begin{cases}
%      1 & \  if \  h_\theta(x) \geq 0.5 \  and \  y=0 \  or\ h_\theta(x) < 0.5 \  and  \  y = 1 \\
%      0 & \ otherwise
%   \end{cases}

%\end{equation}

@@

	Overfittin the data  = low $\lambda$
	\begin{enumerate}
	\item Create a list of lambdas (i.e. $\lambda\in {0,0.01,0.02,0.04,0.08,0.16,0.32,0.64,1.28,2.56,5.12,10.24}$);
\item Create a set of models with different degrees or any other variants.
\item Iterate through the $\lambda$ and for each $\lambda$ go through all the models to learn some $\Theta$.
\item Compute the cross validation error using the learned $\Theta$ (computed with $\lambda$) on the $J_{cv}(\Theta)$ without regularization or $\lambda = 0$.
\item Select the best combo that produces the lowest error on the cross validation set.
\item Using the best combo $\Theta$ and $\lambda$, apply it on $J_{test}(\Theta)$ to see if it has a good generalization of the problem.
	\end{enumerate}

@@

	\begin{enumerate}
	\item Getting more training examples: Fixes high variance
\item Trying smaller sets of features: Fixes high variance
\item Adding features: Fixes high bias
\item Adding polynomial features: Fixes high bias
\item Decreasing $\lambda$: Fixes high bias
\item Increasing $\lambda$: Fixes high variance.
	\end{enumerate}

@@

A large neural network with more parameters is prone to overfitting. It is also computationally expensive. In this case you can use regularization (increase $\lambda$) to address the overfitting.

@@

	Skewed classes: events that are rare in a given set. Example: 0.5 \% of people have cancer.

	The metrics to measure skewed classes are called precision and recall.

	Precision is defined as: 
	\begin{equation}
	precision = \frac{true \ positives}{true \ positives + false \ positives}
	\end{equation}

	Recall is defined as:
	\begin{equation}
	precision = \frac{true \ positives}{true \ positives + false \ negatives}
	\end{equation}

	We can change the threshold value for h for classifying y = 1 or y = 0. if our threshold value is > 0.5, we are valuing confidence, so high \textbf{precision}, lower recall.

	However, the opposite means the false negatives are important and should NOT happen. So, when in doubt, y = 1. You end up with higher recall and lower precision.

	You want precision and recall to be both elevated.

	How to choose the threshold? You can compute the F1 score $2\frac{PR}{P+R}$. There are others too.

	\subsubsection{Week 7}

	Large margin calssifiers

	We can rewrite the cost function to optimize the calculations, choose functions that are very close to the optimal but are easier to calculate.

	For example, the logistic regression cost with Support Vector  Machine (SVM) is known as: SVM hypothesis and is written as follows for the logistic regression problem: 
	\begin{equation}
	min_{\theta} C \sum_{i=1}^{m} [y^{(i)}cost_1(\theta^Tx^{(i)}) + (1- y^{(i)})cost_0(\theta^Tx^{(i)})] + \frac{1}{2}\sum_{j=1}^{n}\theta_j^2
	\end{equation}
	Cost1 and Cost0 are  the linearization of the cost curve.

	The parameter C plays with bias and variance. Large C means lower bias and high variance. While small C means higher bias and low variance.

	So in the end you want to predict the value of y juist basing over the value of $\theta^Tx$.

	\textbf{Kernels: }

	Suppose you have a non-linear decision boundary. Given x, compute new features based on the distance with given landmarks. The functions that calculate is called a similarity function (kernel function) and may be, for example, a gaussian kernel, where:
	\begin{equation}
	f_1=exp(-\frac{||x-l^{(k)}||^2}{2\sigma^2})
	\end{equation}

	Landmark: $l^{(k)}$	. Kernel Function: andmark: $f^{(k)}(x)$.

	With them, we can define new features and make complex boundary curves. Instead of basing ourselves in the product of $\theta^Tx$, we compute $\theta^Tf(x)$ to make our decisions.

	The variance of the kernel plays over bias and variance.

	Large $\sigma^2$: features $f_i$ vary more smoothly, high bias, lower variance.

	Small $\sigma^2$: features $f_i$ vary less smoothly, lower bias, higher variance.

	If SVM is overfittinf your data, it is good to DECREASE C and INCREASE $\sigma^2$.

	There are libraries to solve SVM optimization problems. DO NOT  implement code to optimize stuff, like minimizing for theta.

	To use the algorithms, you should:
	\begin{enumerate}
	\item Choose C.
	\item Choose Kernel (similarity function). If you have lots of features but small training set, than don't use kernels and just use logistic regression).
	\item Choose $\sigma^2$.
	\item Implement the kernel function (DO PERFORM feature scaling before using the Kernel, otherwise one feature will take over).
	\item The choice of a Kernel shoul satisfy "Mercer's Theorem".
	\item Fix the parameter in the ones that gives the best cross validation error.
	\end{enumerate}

	Available Kernels: Polynomial, Gaussian, String, chi-squared, etc. SVM is a convex optimization problem.

	If the number of features is small and the number of training examples is large, create features and then use logistic regression, or a linear Kernel, because PCs struggle to calculate a Gaussian Kernel for example.

	Neural Network should work in all conditions, but should be slower to train.
